---
title: "Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Introduction
This is a versatile R package designed to streamline phonetic transliteration between Hindi and English languages. This package serves as a valuable tool for individuals, researchers, and businesses working with multilingual data or requiring seamless translation between Hindi and English datasets.

# Installation

You can install the sanketphonetictranslator package from CRAN using the following command:
  
```r
install.packages(sanketphonetictranslator)
```

Or you can install the development version from GitHub:
  
```r
remotes::install_github("metalwings-design/SanketPhoneticTranslator")
```

# Usage
To use the package, first load it into your R session:


```{r setup}
library(sanketphonetictranslator)
```


# Dataset Transliteration
You can also transliterate entire datasets using the transliterate_dataset function:
  
  
```r
#load data
data("dataset")
data <- dataset

# Transliterate the dataset from Hindi to English
translated_data <- transliterate_dataset(data, "hindi2english")

# View the first few rows of the translated dataset
head(translated_data)
```
